Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-15 Paper.tex
PoW function complete

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description \\
\midrule
$J_{wordbytes}$ & 4  & Bytes in word. \\
$J_{datasetinit}$ & $2^{30}$ & Bytes in dataset at genesis. \\
$J_{datasetgrowth}$ & $2^{23}$ & Dataset growth per epoch. \\
$J_{cacheinit}$ & $2^{24}$ & Cache growth per epoch. \\
$J_{cachegrowth}$ & $2^{17}$ & Cache growth per epoch. \\
$J_{epoch}$ & 30000 & Blocks per epoch. \\
$J_{mixbytes}$ & 128 & mix length in bytes. \\
$J_{hashbytes}$ & 64 & Hash length in bytes. \\
$J_{parents}$ & 256 & Number of parents of each dataset element. \\
$J_{cacherounds}$ & 3 & Number of rounds in cache production. \\
$J_{accesses}$ & 64 & Number of accesses in hashimoto loop. \\
\bottomrule
\end{tabular*}

@@

\subsection{Proof-of-work function}

>>>>

\begin{tabular*}{\columnwidth}[h]{lrl}
\toprule
Name & Value & Description \\
\midrule
$J_{wordbytes}$ & 4  & Bytes in word. \\
$J_{datasetinit}$ & $2^{30}$ & Bytes in dataset at genesis. \\
$J_{datasetgrowth}$ & $2^{23}$ & Dataset growth per epoch. \\
$J_{cacheinit}$ & $2^{24}$ & Bytes in cache at genesis. \\
$J_{cachegrowth}$ & $2^{17}$ & Cache growth per epoch. \\
$J_{epoch}$ & 30000 & Blocks per epoch. \\
$J_{mixbytes}$ & 128 & mix length in bytes. \\
$J_{hashbytes}$ & 64 & Hash length in bytes. \\
$J_{parents}$ & 256 & Number of parents of each dataset element. \\
$J_{cacherounds}$ & 3 & Number of rounds in cache production. \\
$J_{accesses}$ & 64 & Number of accesses in hashimoto loop. \\
\bottomrule
\end{tabular*}

@@

\subsection{Proof-of-work function}
Essentially, we maintain a "mix" $J_{mixbytes}$ bytes wide, and repeatedly sequentially fetch $J_{mixbytes}$ bytes from the full dataset and use the fnv function to combine it with the mix. $J_{mixbytes}$ bytes of sequential access are used so that each round of the algorithm always fetches a full page from RAM, minimizing translation lookaside buffer misses which ASICs would theoretically be able to avoid.

If the output of this algorithm is below the desired target, then the nonce is valid. Note that the extra application of \texttt{KEC} at the end ensures that there exists an intermediate nonce which can be provided to prove that at least a small amount of work was done; this quick outer PoW verification can be used for anti-DDoS purposes. It also serves to provide statistical assurance that the result is an unbiased, 256 bit number.

In order to formalize this algorithm, we first define a seed hash $\mathbf{s}_h$:
\begin{equation}
 \mathbf{s}_h = \texttt{KEC512}(\mathbf{h} + \mathbf{n}_r)
\end{equation}
With $\mathbf{h}$ being the hash of the header without the nonce, and $\mathbf{n}_r$ the reverted bytes sequence of the nonce:
\begin{equation}
 \mathbf{n}_r[i] =  \mathbf{n}[\lVert \mathbf{n} \rVert -i]
\end{equation}
with $\mathbf{n}$ being the nonce of the header.

The mix $\mathbf{m}$ consists of $n_{mix}$ replicated sequences of $\mathbf{s}_h$.
\begin{equation}
 \mathbf{m}[i] = \mathbf{s}_h \forall 0 \leqslant i < n_{mix}
\end{equation}
\begin{equation}
 n_{mix} =  \left\lfloor\frac{J_{mixbytes}}{J_{hashbytes}}\right\rfloor
\end{equation}
Now we add random dataset nodes to the mix:
\begin{equation}
 \mathbf{m} = E_{accesses}(\mathbf{m}, \mathbf{s}_h, -1)
\end{equation}
\begin{equation}
 E_{accesses}(\mathbf{m}, \mathbf{s}, i) = \begin{cases}
\mathbf{m} & \text{if} \quad i = J_{accesses} -2 \\
E_{accesses}(E_{mixDataset}(\mathbf{m}), \mathbf{s}, i + 1) & \text{otherwise}
\end{cases}
\end{equation}
\begin{equation}
 (E_{mixDataset}(\mathbf{m}, \mathbf{s}, i) = E_\text{\tiny FNV}(\mathbf{m}, E_{newdata}(\mathbf{m}, \mathbf{s}, i))
\end{equation}
\begin{equation}
 E_{newdata}(\mathbf{m}, \mathbf{s}, i)[j] = \mathbf{d}[E_\text{\tiny FNV}(i \oplus \mathbf{s}[0], \mathbf{m}[i \mod \left\lfloor\frac{J_{mixbytes}}{J_{wordbytes}}\right\rfloor) \mod \left\lfloor\frac{d_{size} / J_{hashbytes}}{n_{mix}}\right\rfloor \cdot n_{mix} + j]
\end{equation}
The mix $\mathbf{m}$ is now compressed as follows:
\begin{equation}
 \mathbf{m}_c = E_{compress}(\mathbf{m}, -4)
\end{equation}
\begin{equation}
 E_{compress}(\mathbf{m}, i) = \begin{cases}
\mathbf{m} & \text{if} \quad i \geqslant \lVert \mathbf{m} \rVert - 8 \\
E_{compress}(E_\text{\tiny FNV}(E_\text{\tiny FNV}(E_\text{\tiny FNV}(\mathbf{m}[i], \mathbf{m}[i + 1]), \mathbf{m}[i + 2]), \mathbf{m}[i + 3]), i + 4) & \text{otherwise}
\end{cases}
\end{equation}
Finally the PoW-function can be defined as an array with the compressed mix as its first item and the Keccak-256 hash of the concatenation of the compressed mix with the seed hash as the second item:
\begin{equation}
 \mathtt{PoW}(H, H_n, \mathbf{d}) = \lbrace  \mathbf{m}_c, \texttt{KEC}(\mathbf{s} + \mathbf{m}_c) \rbrace
\end{equation}
